### 2021-04-04 HW-AlgebraicTopology2020/algtop1/algtop1.tex
Restructure to gather quick notes
Add various format tweaks

	\begin{enumerate}
	\item $X$ contractible: $\idty_X \simeq f_0\colon X\to X$ some constant map, $f_0(X) = \{x_0\}$. We can restrict the codomain of $f_0$ so that $f_0\colon X\to\{x_0\}$, in this way we have:
	\begin{subequations}
	\renewcommand{\theequation}{\theparentequation.\arabic{equation}}
	\begin{align}
		X\xrightarrow{f_0} \{x_0\}
			\hookrightarrow X
		&\simeq \idty_X,
		\label{eq:homotopy_on_X}\\
		\{x_0\}\hookrightarrow X
			\xrightarrow{f_0} \{x_0\}
		&\simeq \idty_{\{x_0\}},
	\end{align}
	\label{eq:homotopic_equiv}
	\end{subequations}
	This means that $f_0\colon X\to\{x_0\}$ isomorphic in $\Cat{hTop} = \Cat{Top}/\simeq$, which is precisely the definition of homotopic equivalence $X\simeq\{x_0\}$. ($\Rightarrow$)

@@

	\item \textbf{Fundamental group of topological group is abelian}\footnote{%
		This proof is produced with the help of \https{math.stackexchange.com/q/727999}. 
	}:

>>>>

	\begin{enumerate}
	\item $X$ contractible: $\idty_X \simeq f_0\colon X\to X$ some constant map, $f_0(X) = \{x_0\}$. We can restrict the codomain of $f_0$ so that $f_0\colon X\to\{x_0\}$, in this way we have:
	\begin{subequations}
	\renewcommand{\theequation}{\theparentequation.\arabic{equation}}
	\begin{align}
		X\xrightarrow{f_0} \{x_0\}
			\hookrightarrow X
		&\simeq \idty_X,
		\label{eq:homotopy_on_X}\\
		\{x_0\}\hookrightarrow X
			\xrightarrow{f_0} \{x_0\}
		&\simeq \idty_{\{x_0\}},
	\end{align}
	\label{eq:homotopic_equiv}
	\end{subequations}
	\\[-\baselineskip]
	This means that $f_0\colon X\to\{x_0\}$ isomorphic in $\Cat{hTop} = \Cat{Top}/\simeq$, which is precisely the definition of homotopic equivalence $X\simeq\{x_0\}$. ($\Rightarrow$)

@@

	\item \textbf{Fundamental group of topological group is abelian}\footnote{%
		This proof is produced with the help of \https{math.stackexchange.com/q/727999}. Another (easier) proof lies in the fact that group translation induces $\pi_1$ conjugation, therefore $\gamma^{-1} \alpha \gamma = \alpha$, hence abelian. 
	}:
